\Large \bf On semidefinite-representable sets over valuation fields

### 2025-05-23 article/paper_padic_spec.tex
commit by Simone

The study of polyhedra and of linear programming (LP) is at the heart of convex geometry and optimization,
inasmuch as several optimization problems can be cast as, or relaxed to LP. An important generalization of LP
is semidefinite programming (SDP), namely the problem of minimizing an affine polynomial over the set of
positive semidefinite affine combinations of a given collection of real symmetric matrices. The latter problem 
has interested the community of real algebraic geometry and polynomial optimization, mostly because of the
relaxation method known as moment-SOS (or Lasserre) hierarchy \cite{henrion2020moment}.

>>>>

The study of polyhedra and of linear programming (LP) is at the heart of convex geometry and optimization, inasmuch as several optimization problems can be cast as, or relaxed to LP. An important generalization of LP is semidefinite programming (SDP), namely the problem of minimizing a linear function over the set of positive semidefinite affine combinations of some real symmetric matrices. The latter problem has interested the community of real algebraic geometry and polynomial optimization, mostly because of the relaxation method known as moment-SOS (or Lasserre) hierarchy \cite{henrion2020moment}.
